---
title: "Data Products W3: Plotly Charts"
author: "Axel Garcia"
date: "February 15th, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(plotly)
knitr::opts_chunk$set(echo = FALSE)
```

## Chart 1 of 2: Scatter Plot (2D Chart)
```{r plotly2, echo=FALSE, message=FALSE, warning=FALSE}
attach(attitude)
plot_ly(attitude, x=complaints, y=raises, type="scatter", mode="markers", color=advance, size=learning) %>%
  layout(
    title="The Chatterjee–Price Attitude Data",
    xaxis=list(title="employee complaints"),
    yaxis=list(title="Raises based on performance")
  )
```

* Size is Opportunity to learn
* Color is Advancement

## Chart 2 of 2: Scatter Plot (3D Chart)
```{r plotly1, echo=FALSE, message=FALSE, warning=FALSE}
attach(freeny)
plot_ly(freeny, x=time(y), y=income.level, z=price.index, 
        type="scatter3d", mode="markers", color=market.potential,
        size=lag.quarterly.revenue+100) %>% 
  layout(
    title="Freeny's Revenue Data",
    scene=list(
      xaxis=list(title="Time"), 
      yaxis=list(title="Income Level"),
      zaxis=list(title="Price Index"))
    )
```
* Clear correlation between Income Level and Price Index over time.

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
